### 2022-09-17 main/chapter_searches.tex
change to paragraph for cr vr sr

\paragraph{CR, VR, SR.}
\atlas\ SUSY searches see data only through discrete histogram bins,
or `regions', which are defined by logical selections in event variables.
To communicate their intended uses, we further categorize these bins into
`control', `validation', and `signal' regions.

\textbf{Control regions} (\textbf{CR}s), select large numbers data to
constrain global normalization factors that scale the major
Standard Model backgrounds;
these normalization factors control the total cross-sections of
background samples while preserving their relatives shapes between regions.
Disregarding theoretical Standard Model cross-sections is justified, since
the control region constraints are, by design, more precise than any previous
estimate local to our regions.

To represent the Standard Model, control regions must be insensitive to
non-standard signals.
Before applying their normalization factors to regions that are sensitive
to signal hypotheses, data in \textbf{validation regions} (\textbf{VR}s) first
test the quality of extrapolation.
Each model is adjusted until validation region data are well predicted ---
either by changing region definitions or restructuring the \heplikelihood\
model, perhaps with extrapolation uncertainties or extra normalization
factors.
Likelihoods for validation region data are not included in the \heplikelihood\
models, but their data are important and indirectly used to update the
model in this manner.

Consuming information from control and validation regions to refine the
predictions of our background-only model is scientific learning, and can be
reconciled with machine learning practice as fitting a model with training
(CR) and validation (VR) data.
Testing is performed through in prediction of data in the
\textbf{signal regions} (\textbf{SR}s),
in which signal yields should significantly add on top of the Standard Model
backgrounds.
Some signal regions are also labelled \textbf{DR} to indicate their use in
specific `discovery' fits.

>>>>

Our searches see data only through discrete histogram bins,
or `regions', which are defined by logical selections in event variables.
To communicate their intended uses, we further categorize these bins into
`control', `validation', and `signal' regions.

\paragraph{Control regions (CRs).}
Control regions select large numbers data to
constrain global normalization factors that scale the major
Standard Model backgrounds;
these normalization factors control the total cross-sections of
background samples while preserving their relatives shapes between regions.
Disregarding theoretical Standard Model cross-sections is justified, since
the control region constraints are, by design, more precise than any previous
estimate local to our regions.

\paragraph{Validation regions (VRs).}
To represent the Standard Model, control regions must be insensitive to
non-standard signals.
Before applying their normalization factors to regions that are sensitive
to signal hypotheses, data in \textbf{validation regions} (\textbf{VR}s) first
test the quality of extrapolation.
Each model is adjusted until validation region data are well predicted ---
either by changing region definitions or restructuring the \heplikelihood\
model, perhaps with extrapolation uncertainties or extra normalization
factors.
Likelihoods for validation region data are not included in the \heplikelihood\
models, but their data are important and indirectly used to update the
model in this manner.

\paragraph{Signal regions (SRs).}
Consuming information from control and validation regions to refine the
predictions of our background-only model is scientific learning, and can be
reconciled with machine learning practice as fitting a model with training
(CR) and validation (VR) data.
Testing is performed through in prediction of data in the
\textbf{signal regions} (\textbf{SR}s),
in which signal yields should significantly add on top of the Standard Model
backgrounds.
Some signal regions are also labelled \textbf{DR} to indicate their use in
specific `discovery' fits.
